\textbf{Evaluating RISC-V Enclaves:}\\ Security Without the Slowdown?

### 2025-09-03 draft_presentation.tex
improved best practices section

% Optimizations for Keystone Enclaves
\begin{frame}{Optimizations for Keystone Enclaves}
\begin{itemize}
    \item Use contiguous, NAPOT-aligned memory to minimize PMP usage.
    \item Consolidate workloads and limit active enclaves to reduce contention.
    \item Offload non-sensitive tasks to the untrusted domain.
\end{itemize}
\end{frame}

@@

% Future Work and Improvements
\begin{frame}{Future Work and Improvements}
\begin{itemize}
    \item Performance optimizations with hardware extensions.
    \item Multi-enclave systems for more complex use cases.
    %\item Research on side-channel attacks and improved security measures.
    \item Development of better developer tools for enclave management.
\end{itemize}
\end{frame}

@@

\begin{frame}{Summary of Findings}
\begin{itemize}
    \item \textbf{Keystone offers low-overhead enclaves} for CPU-bound workloads.
    \item \textbf{Memory-bound performance degrades} due to PMP overhead and context switching.
    \item \textbf{Scalability limited} by fixed PMP entries and misaligned region padding.
    \item \textbf{Performance can be improved} via alignment and workload partitioning strategies.
\end{itemize}
\end{frame}

>>>>

% Optimizations for Keystone Enclaves
% \begin{frame}{Optimizations for Keystone Enclaves}
% \begin{itemize}
%     \item Use contiguous, NAPOT-aligned memory to minimize PMP usage.
%     \item Consolidate workloads and limit active enclaves to reduce contention.
%     \item Offload non-sensitive tasks to the untrusted domain.
% \end{itemize}
% \end{frame}

\begin{frame}{Deployment Takeaways}
\begin{block}{Best Practices}
\begin{itemize}
    \item Use NAPOT-aligned, contiguous memory regions.
    \item Consolidate workloads into fewer enclaves.
    \item Batch calls to reduce context switches.
\end{itemize}
\end{block}

\begin{alertblock}{Key Principle}
Balance performance, isolation, and PMP resource use.
\end{alertblock}
\end{frame}

% \begin{frame}{Memory Configuration Strategies}
% \begin{block}{Key Practices}
% \begin{itemize}
%     \item Use \textbf{NAPOT-aligned, contiguous memory} for enclaves.
%     \item Avoid fragmentation to conserve PMP entries.
% \end{itemize}
% \end{block}

% \begin{block}{Trade-Offs}
% \begin{itemize}
%     \item Larger regions improve performance (fewer faults, better locality).
%     \item But excessive size leads to wasted PMP entries.
% \end{itemize}
% \end{block}
% \end{frame}

% \begin{frame}{CPU Scaling Considerations}
% \begin{block}{Observations}
% \begin{itemize}
%     \item Performance improves up to \textasciitilde{}4 cores.
%     \item Beyond that, overhead from context switches and sync dominates.
% \end{itemize}
% \end{block}

% \begin{alertblock}{Recommendation}
% Use enclaves for \textbf{compute-bound workloads} (e.g., CoreMark), not memory-bound ones (e.g., Kyber).
% \end{alertblock}
% \end{frame}

\begin{frame}{Workload-Aware Enclave Design}
\begin{block}{Hybrid Cryptographic Workloads}
\begin{itemize}
    \item Keep keys inside enclaves.
    \item Offload bulk crypto outside to reduce overhead.
\end{itemize}
\end{block}

\begin{block}{Target Use Cases}
\begin{itemize}
    \item Isolate sensitive logic (e.g., ML inference, attestation).
    \item Avoid enclaves for memory-bound workloads like Kyber.
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{Enclave Concurrency and Multiplexing}
\begin{block}{Problem}
Too many active enclaves → PMP exhaustion, context switch cost.
\end{block}
\begin{alertblock}{Solution}
Use enclave multiplexing: combine tasks into fewer enclaves.
\end{alertblock}
\begin{block}{Bonus}
Dynamic PMP reallocation can further improve scalability.
\end{block}
\end{frame}

% \begin{frame}{Runtime Optimization}
% \begin{block}{Key Ideas}
% \begin{itemize}
%     \item \textbf{Batch enclave calls} to reduce switch overhead.
%     \item Use \textbf{dynamic PMP assignment} based on active workloads.
% \end{itemize}
% \end{block}

% \begin{block}{Lifecycle Management}
% \begin{itemize}
%     \item Reuse enclaves across tasks.
%     \item Scale resources based on current demand.
% \end{itemize}
% \end{block}
% \end{frame}

@@

% Future Work and Improvements
\begin{frame}{Hardware Outlook \& Future Directions}
\begin{block}{Limitations}
\begin{itemize}
    \item Few PMP entries.
    \item Rigid NAPOT region encoding.
\end{itemize}
\end{block}

\begin{alertblock}{Future Opportunities}
\begin{itemize}
    \item More flexible PMP schemes.
    \item Crypto accelerators for enclave workloads.
    \item Software-defined memory isolation models.
\end{itemize}
\end{alertblock}
\end{frame}

@@

% \begin{frame}{Summary of Best Practices}
% \begin{block}{Configuration Tips}
% \begin{itemize}
%     \item Use \textbf{NAPOT-aligned contiguous memory}.
%     \item \textbf{Limit concurrent enclaves}; favor multiplexing.
%     \item Offload non-sensitive tasks.
%     \item Batch calls, manage PMP dynamically.
% \end{itemize}
% \end{block}

% \begin{alertblock}{Design Principles}
% \textbf{Balance} isolation, performance, and scalability.
% \end{alertblock}
% \end{frame}
